Deterministic contention management for low latency Cloud RAN over an optical ring

### 2019-01-17 v3/articleV3.tex
modif fulfill pos

In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow. In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packet insertions on the ring, with or without priority for C-RAN packets. In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees to have zero latency from buffering. We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packets.

@@

\section{Deterministic approach for zero latency} \label{sec:deterministicalgorithms}

Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}. In this section, we give a simple solution to this problem in the N-GREEN optical ring, and we adapt it to minimize the latency of the BE traffic.

@@

\section{A smarter approach for N-GREEN parameters}
\label{sec:maxant}

@@

In order to allow as much antennas as possible on the ring, the idea is to use \emph{all} containers in a given position. To do so we do the compacting positions of previous section and when less than $ET$ free containers remain in a position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position. Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas. The number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$.

@@

>>>>

In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow. In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packet insertions on the ring, with or without priority for C-RAN packets. In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees to have zero latency from buffering. We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packet, or to allow the ring to support a maximal number of antennas, regardless the parameters.

@@

\section{Deterministic approach for zero latency} \label{sec:deterministicalgorithms}
\subsection{Reservation, assignment}
Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}. In this section, we give a simple solution to this problem in the N-GREEN optical ring, and we adapt it to minimize the latency of the BE traffic.

@@

\subsection{A smarter approach for N-GREEN parameters}
\label{sec:maxant}

@@

\paragraph{Fulfilling positions}
In order to allow as much antennas as possible on the ring, the idea is to use \emph{all} containers in a given position. To do so we assign the antennas to the first position which is not full. When less than $ET$ free containers remain in this position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position. Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas.

Remark that we consider only the even positions, because the BBU are set by definitions on the odd positions. This mean that a container reserved to the next position means in reality that this container is reserved $2$ positions after. Thus, a message arriving in a node from an RRH at time $m_i$ can see its reserved container at time $m_i +2$ which introduce a bit of additional latency of $2\mu$s for a part of the CRAN traffic. However, the number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$, which is a considerable gain with our N-GREEN parameters ($9$ antennas instead of $5$).

@@

  Since the N-GREEN parameters only allows to do balancing into the period of the previous section, we want to compare the impact on the best effort traffic of fulfilling positions against balancing into the period and FIFO rule. 
Fig.~\ref{fig:splitres} represent the cumulative distribution of the best effort traffic with those three methods, and with the N-GREEN parameters.

      \includegraphics[scale=0.25]{splitres}
     \caption{Impact of fulfilling positions on BE traffic.}   \label{fig:splitres}
\end{center}
  \end{figure}
